%-------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}

\begin{cventries}

  \cventry
    {NASA Space Technology Graduate Researcher (NSTGRO Fellow)}
    {NASA --- National Aeronautics and Space Administration}
    {Boulder, CO, USA (Remote / NASA collaboration)}
    {Jul.\ 2022 -- Present}
    {
      \begin{cvitems}
        \item Awarded the NSTGRO fellowship (Grant 80NSSC22K1211) for research on fail-active manipulation in space-relevant scenarios where human rescue is infeasible.
        \item Collaborate with \href{https://www.nasa.gov/reference/jsc-robotics/}{NASA JSC Robotics} on long-term reliability and graceful degradation of robotic systems.
      \end{cvitems}
    }

  \cventry
    {Graduate Research Assistant}
    {HIRO Group, University of Colorado Boulder}
    {Boulder, CO, USA}
    {Aug.\ 2021 -- Present}
    {
      \begin{cvitems}
        \item Advised by \href{https://hiro-group.ronc.one/}{Prof.\ Alessandro Roncone}.
        \item Lead author on the lab's \textit{fail-active manipulation} research thread: an embodiment-conditioned diffusion policy (DEFT, ICRA'26) that recovers from arbitrary joint failures on a 7-DoF Franka Panda --- 99.5\% / 46.4\% success on unconstrained / constrained motion across 4.7M trajectories \& 4.7k failure conditions, with 10/10 real-world task completion.
        \item Earlier work: non-prehensile failure recovery (IROS'24) showing up to \textbf{79\%} workspace expansion and \textbf{88.9\%} task success without a functional end-effector.
        \item Co-author on CERG (IFAC'26), a collaboration with the \href{https://www.colorado.edu/faculty/nicotra/robotics-optimization-and-constrained-control}{ROCC Lab} (Prof.\ Marco M.\ Nicotra) on compliant contact-rich control.
        \item Co-author on PBD-R (arXiv:2603.14634), a particle-based simulator with physically accurate rigid-body dynamics for sim-to-real transfer.
      \end{cvitems}
    }

  \cventry
    {Undergraduate Researcher}
    {Human Centered Robotics Lab (HCRL), UT Austin Aerospace Engineering \& Engineering Mechanics}
    {Austin, TX, USA}
    {Jan.\ 2018 -- May 2021}
    {
      \begin{cvitems}
        \item Multi-year undergraduate research role (Prof.\ Luis Sentis) spanning perception, planning, and task execution for service robots in human environments.
        \item Member of the \textbf{UT Austin Villa @ Home} RoboCup team --- co-authored the AAAI AI-HRI 2019 team report.
      \end{cvitems}
    }

\end{cventries}
